Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2021-01-02 submission/NatCom_all_models.tex
trying to include table 3
table 3 updated

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1.25in}|c|c|c|c|}
\hline
%    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
%    & $\langle\log\Vert\mathbf{W}\Vert_{F}\rangle$ & $\langle\log\Vert\mathbf{W}\Vert_{\infty}\rangle$ & $\langle\hat{\alpha}=\alpha\log\lambda_{max}\rangle$ & $\langle\log\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ \\
                        & $\log\Vert\cdot\Vert_{F}$ & $\log\Vert\cdot\Vert_{\infty}$ & $\hat{\alpha}$ & $\log\Vert\cdot\Vert^{\alpha}_{\alpha}$ \\
\hline
$R^{2}$ (mean)          & 0.63 &  0.55 & \textbf{0.64} & \textbf{0.64} \\
$R^{2}$ (std)           & 0.34 &  0.36 & \textbf{0.29} &          0.30 \\
\hline
$MSE$ (mean)            & 4.54 &  9.62 &          3.14 & \textbf{2.92} \\
$MSE$ (std)             & 8.69 & 23.06 &          5.14 & \textbf{5.00} \\
\hline
Kendall-$\tau$ (mean)   &  XXX &   XXX &           XXX &           XXX \\
Kendall-$\tau$ (std)    &  XXX &   XXX &           XXX &           XXX \\
\hline
\end{tabular}
\end{center}
\caption{Comparison of linear regression fits for different average Log Norm and Weighted Alpha metrics across 5 CV datasets, 17 architectures, covering 108 (out of over 400) different pretrained DNNs.  
         We include regressions only for architectures with five or more data points, and which are positively correlated with test error.
         These results can be readily reproduced using the Google Colab notebooks. 
         (See the Supplementary Information
         %~\ref{sxn:appendix} 
         for details.) 
        }
\label{table:results}
\end{table}

>>>>

\input{table_3}
\charles{Tabel 3 is autogenerated now: I think R2 adjusted may be a better statistic for us}
